\sysfull

### 2017-08-04 paper/compiler.tex
added sensitivity result

\sys provides compiler support for \emph{automatic task generation} that simplifies programming writing task-based code by automatically translating C code into a task-based executable.  Translating C code into task-based code automatically requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task, or are made explicit in inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime.  The \sys compiler first analyzes the control-flow graph (CFG) and, using a rule-based heuristic, determines at which points to place a task boundary.  After identifying where to put task boundaries, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.

@@

\subsubsection{Task Boundary Placement}

@@

The analysis uses a heuristic to compute a score for each candidate and places
a boundary at the candidate with the highest score. The heuristic tries to
avoid placing boundaries on loops, to minimize the number of live variables
that must be protected across the new boundary, and to maximize the number of
operations along the path.  A boundary candidate's score is computed as:
%
\begin{equation}
\text{score} = \frac{w_{0} N_{\text{IR}} - w_{1} N_{\text{PV}}}{N_{\text{loop}}},\nonumber
\end{equation}
%
where $N_{\text{IR}}$ is the length of the path being traversed up to the
candidate, $N_{\text{PV}}$ is the number of variables live variables at the
candidate, and $N_{\text{loop}}$ is the product of the loop bounds of all loops
(i.e., nested loops) containing the boundary candidate. \sys normalizes $N_{\text{IR}}$ to the
total number of instructions along the path being traversed. The weights, $w_{0},
w_{1}$ are between zero and one, and are hand-tuned parameters that define the
relative importance of $N_{\text{IR}}$, $N_{\text{PV}}$, and $N_{\text{loop}}$.
We will study the effect of weights in Section~\ref{sec:results_compiler}.

@@

>>>>

\sys provides compiler support for \emph{automatic task generation} that simplifies writing task-based code by automatically translating C code into a task-based executable.  Translating C code into task-based code automatically requires identifying program points to use as task boundaries, defining a set of task functions that begin and end at those boundaries, ensuring that all existing control-flow paths are either contained within a task, or are made explicit in inter-task control-flow, and identifying and instrumenting accesses to task-shared variables that need to be protected by \sys at runtime.  The \sys compiler first analyzes the control-flow graph (CFG) and, using a rule-based heuristic, determines at which points to place a task boundary.  After identifying where to put task boundaries, the \sys compiler transforms the imperative code into tasks, instrumenting protected memory accesses.

@@

\subsubsection{Task Boundary Placement}
\label{sec:compiler_boundary}

@@

The analysis uses a heuristic to compute a score for each candidate and places
a boundary at the candidate with the highest score. The heuristic tries to
avoid placing boundaries on loops, to minimize the number of live variables
that must be protected across the new boundary, and to maximize the number of
operations along the path.  A boundary candidate's score is computed as:
%
\begin{equation}
\text{score} = \frac{w_{0} N_{\text{IR}} - w_{1} N_{\text{PV}}}{N_{\text{loop}}},\nonumber
\end{equation}
%
where $N_{\text{IR}}$ is the length of the path being traversed up to the
candidate, $N_{\text{PV}}$ is the number of variables live variables at the
candidate, and $N_{\text{loop}}$ is the product of the loop bounds of all loops
(i.e., nested loops) containing the boundary candidate. \sys normalizes $N_{\text{IR}}$ to the
total number of instructions along the path being traversed. The weights, $w_{0},
w_{1}$ are between zero and one, and are hand-tuned parameters that define the
relative importance of $N_{\text{IR}}$, $N_{\text{PV}}$, and $N_{\text{loop}}$.
We will study the effect of weights in Section~\ref{sec:compiler_heuristics}.

@@

\subsection{Boundary Placement Heuristics}
\label{sec:compiler_heuristics}

By studing different weights discussed in Section~\ref{sec:compiler_boundary},
we discovered that there is no one global weights that are optimal for every
application, and more importantly, the weights do not matter much and
result in less than 5\% run time difference. The result is mainly because
no matter what the weight is, we place boundaries at obvious points (such as back-edge of a
large loop) and we never place boudaries at obviously-bad points (such as
inside a loop when the loop is not large). Since these obvious decision
dominates the structure of tasks and heuristics only give minute perturbation,
the result does not gets affected significantly.
As an extreme, for small apps like CEM, only placing boundaries at obvious points are enough to
determine the entire task structure. It never needs any additional heuristics.
We used weight of 
$w_{0} = 0.5$ and $w_{1} = 0.5$ for the experiment result in Section~\ref{sec:experiment}.
